### 2019-08-15 dantzig_selector/presentation_A/5_slide.tex
Code: Correct normalizing constants

\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a explicit constant
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Future Work}
{
\I Check the proof carefullly, especially approximation

@@

\I Also implement OMP and compare they two
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {References}
{
{\tfxx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

>>>>

\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a constant explicit depending on system parameters \m {s} and \m{L}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Future Work}
{
\I Check the proof carefullly, especially the approximation technique

@@

\I Also implement OMP and compare they two
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {References}
{
{\tfx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.
